### 2012-10-21 paper_sean/robot.tex
updated footnote

We performed the experiments on the QuadraTot quadrupedal robot platform~(\figref{quadratotWhiteBooties}).
It has 9 degrees-of-freedom (DOF): two joints per leg and one joint that allowed rotation along the robot's midline. %we def want a picture of the cool robot. I propose putting the picture of the robot on the left and the picture of the simulated robot on the right of the same figure. That also does a nice job of highlighting the theme of the paper (robot+sim) in one figure. Try to get this figure to show up as early as possible in the paper (e.g top of the 2nd page). 
The QuadraTot hardware designs and software for this project are open source\footnote{A list of all of the parts and all software, including the simulator, is available for free at http://creativemachines.cornell.edu/evolved-quadruped-gaits}, and all hardware components are either off-the-shelf or 3D printed parts. These traits enable other labs to perform research using the same platform, which eases comparison of different gait-learning algorithms. 
To date there are results on the platform from nine different learning algorithms from three previous publications~\cite{yos:clune,glette,haocheng}. We identified the robot's position using an infrared LED on the robot which was tracked using a Wiimote~\cite{yos:clune}.

>>>>

We performed the experiments on the QuadraTot quadrupedal robot platform~(\figref{quadratotWhiteBooties}).
It has 9 degrees-of-freedom (DOF): two joints per leg and one joint that allowed rotation along the robot's midline. %we def want a picture of the cool robot. I propose putting the picture of the robot on the left and the picture of the simulated robot on the right of the same figure. That also does a nice job of highlighting the theme of the paper (robot+sim) in one figure. Try to get this figure to show up as early as possible in the paper (e.g top of the 2nd page). 
The QuadraTot hardware designs and software for this project are open source\footnote{A parts list, hardware CAD files, software (including the simulator), and gait videos are available at http://creativemachines.cornell.edu/evolved-quadruped-gaits}, and all hardware components are either off-the-shelf or 3D printed parts. These traits enable other labs to perform research using the same platform, which eases comparison of different gait-learning algorithms. 
To date there are results on the platform from nine different learning algorithms from three previous publications~\cite{yos:clune,glette,haocheng}. We identified the robot's position using an infrared LED on the robot which was tracked using a Wiimote~\cite{yos:clune}.
